### 2015-06-01 alubp.tex
removed vspaces

||J^*-\hg J^*||_\infty&\leq||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty\nn\\\vspace{10pt}

@@

&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\\vspace{10pt}

@@

\begin{corollary}\label{cmt1}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_\infty$, then
\begin{align}
||J^*-\hv||_\infty\leq \frac{2||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{corollary}
\begin{proof}
The result is obtained by using Lemma~\ref{bestbnd} to replace the term $||J^*-\bj||_\infty$ in Theorem~\ref{mt1}.
\end{proof}

>>>>

||J^*-\hg J^*||_\infty&\leq||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty\nn\\

@@

&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\

@@

\begin{corollary}\label{cmt1}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_\infty$, then
||J^*-\hv||_\infty\leq \frac{2||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{corollary}
The result is obtained by using Lemma~\ref{bestbnd} to replace the term $||J^*-\bj||_\infty$ in Theorem~\ref{mt1}.
